Improving the portuguese hyphenation rules

### 2024-06-14 article/comparedresults.tex
updates

@@

@@

diário & di-á*ri*o \xmark & di*á*ri*o \cmark \\
diária & di-á*ri*a \xmark & di*á*ri*a \cmark \\
judiciário & ju*di*ci-á*ri*o \xmark & ju*di*ci*á*ri*o \cmark \\
influência & in*flu-ên*ci*a \xmark & in*flu*ên*ci*a \cmark \\
depoimento & de*po-i*men*to \xmark & de*po-i*men*to \xmark \\
instituição & ins*ti*tu-i*ção \xmark & ins*ti*tu*i*ção \cmark \\
consequência & con*se-quên*ci*a \xmark & con*se*quên*ci*a \cmark \\
usuário & u*su-á*ri*o \xmark & u*su*á*ri*o \cmark \\
continuidade & con*ti*nu-i*da*de \xmark & con*ti*nu*i*da*de \cmark \\
sequência & se-quên*ci*a \xmark & se*quên*ci*a \cmark \\
poluição & po*lu-i*ção \xmark & po*lu*i*ção \cmark \\
proibido & pro-i*bi*do \xmark & pro*i*bi*do \cmark \\
frequência & fre-quên*ci*a \xmark & fre*quên*ci*a \cmark \\
proibição & pro-i*bi*ção \xmark & pro*i*bi*ção \cmark \\
crediário & cre*di-á*ri*o \xmark & cre*di*á*ri*o \cmark \\
coincidência & co-in*ci*dên*ci*a \xmark & co*in*ci*dên*ci*a \cmark \\
noticiário & no*ti*ci-á*ri*o \xmark & no*ti*ci*á*ri*o \cmark \\
imobiliário & i*mo*bi*li-á*ri*o \xmark & i*mo*bi*li*á*ri*o \cmark \\
penitenciária & pe*ni*ten*ci-á*ri*a \xmark & pe*ni*ten*ci*á*ri*a \cmark \\
psicologia & p.si*co*lo*gi*a \xmark & psi*co*lo*gi*a \cmark \\
aéreo & a-é*re*o \xmark & a*é*re*o \cmark \\
vestuário & ves*tu-á*ri*o \xmark & ves*tu*á*ri*o \cmark \\
constituinte & cons*ti*tu-in*te \xmark & cons*ti*tu-in*te \xmark \\
imobiliária & i*mo*bi*li-á*ri*a \xmark & i*mo*bi*li*á*ri*a \cmark \\
rodoviário & ro*do*vi-á*ri*o \xmark & ro*do*vi*á*ri*o \cmark \\
proibir & pro-i*bir \xmark & pro*i*bir \cmark \\
baía & ba-í-a \xmark & ba*í*a \cmark \\
raiz & ra-iz \xmark & ra-iz \xmark \\

@@

vestiário & ves*ti-á*ri*o \xmark & ves*ti*á*ri*o \cmark \\
intermediário & in*ter*me*di-á*ri*o \xmark & in*ter*me*di*á*ri*o \cmark \\
penitenciário & pe*ni*ten*ci-á*ri*o \xmark & pe*ni*ten*ci*á*ri*o \cmark \\
mutuário & mu*tu-á*ri*o \xmark & mu*tu*á*ri*o \cmark \\
viário & vi-á*ri*o \xmark & vi*á*ri*o \cmark \\
beneficiário & be*ne*fi*ci-á*ri*o \xmark & be*ne*fi*ci*á*ri*o \cmark \\
balneário & bal*ne-á*ri*o \xmark & bal*ne*á*ri*o \cmark \\
pecuária & pe*cu-á*ri*a \xmark & pe*cu*á*ri*a \cmark \\
santuário & san*tu-á*ri*o \xmark & san*tu*á*ri*o \cmark \\
previdenciário & pre*vi*den*ci-á*ri*o \xmark & pre*vi*den*ci*á*ri*o \cmark \\
psiquiatria & p.si*qui*a*tri*a \xmark & psi*qui*a*tri*a \cmark \\
aquário & a-quá*ri*o \xmark & a*quá*ri*o \cmark \\
amendoim & a*men*do-im \xmark & a*men*do-im \xmark \\
ferroviário & fer*ro*vi-á*ri*o \xmark & fer*ro*vi*á*ri*o \cmark \\
mobiliário & mo*bi*li-á*ri*o \xmark & mo*bi*li*á*ri*o \cmark \\
pneumonia & p.neu*mo*ni*a \xmark & pneu*mo*ni*a \cmark \\
anuário & a*nu-á*ri*o \xmark & a*nu*á*ri*o \cmark \\
macedônia & ma*ce-dô*ni*a \xmark & ma*ce*dô*ni*a \cmark \\
oásis & o-á*sis \xmark & o*á*sis \cmark \\
ideário & i*de-á*ri*o \xmark & i*de*á*ri*o \cmark \\
fluência & flu-ên*ci*a \xmark & flu*ên*ci*a \cmark \\
delinquência & de*lin-quên*ci*a \xmark & de*lin*quên*ci*a \cmark \\
receituário & re*cei*tu-á*ri*o \xmark & re*cei*tu*á*ri*o \cmark \\
comerciário & co*mer*ci-á*ri*o \xmark & co*mer*ci*á*ri*o \cmark \\
psicoterapia & p.si*co*te*ra*pi*a \xmark & psi*co*te*ra*pi*a \cmark \\
portuário & por*tu-á*ri*o \xmark & por*tu*á*ri*o \cmark \\
reiniciar & re-i*ni*ci*ar \xmark & re-i*ni*ci*ar \xmark \\
reurbanização & re-ur*ba*ni*za*ção \xmark & re-ur*ba*ni*za*ção \xmark \\
resquício & res-quí*ci*o \xmark & res*quí*ci*o \cmark \\
confluência & con*flu-ên*ci*a \xmark & con*flu*ên*ci*a \cmark \\
guaíba & gua-í*ba \xmark & gua*í*ba \cmark \\
intuitivo & in*tu-i*ti*vo \xmark & in*tu*i*ti*vo \cmark \\
orquídea & or-quí*de*a \xmark & or*quí*de*a \cmark \\
semiótica & se*mi-ó*ti*ca \xmark & se*mi*ó*ti*ca \cmark \\
czar & c.zar \xmark & czar \cmark \\
diluição & di*lu-i*ção \xmark & di*lu*i*ção \cmark \\
eloquência & e*lo-quên*ci*a \xmark & e*lo*quên*ci*a \cmark \\
abruptamente & a.b-rup*ta*men*te \xmark & a.b-rup*ta*men*te \xmark \\
antiquário & an*ti-quá*ri*o \xmark & an*ti*quá*ri*o \cmark \\
tchau & t.chau \xmark & tchau \cmark \\
descontinuidade & des*con*ti*nu-i*da*de \xmark & des*con*ti*nu*i*da*de \cmark \\
anuência & a*nu-ên*ci*a \xmark & a*nu*ên*ci*a \cmark \\
ofurô & o*fu-rô \xmark & o*fu*rô \cmark \\
estagiário & es*ta*gi-á*ri*o \xmark & es*ta*gi*á*ri*o \cmark \\

@@

presidiário & pre*si*di-á*ri*o \xmark & pre*si*di*á*ri*o \cmark \\
antiético & an*ti-é*ti*co \xmark & an*ti*é*ti*co \cmark \\
píer & pí-er \xmark & pí-er \xmark \\
atônito & a-tô*ni*to \xmark & a*tô*ni*to \cmark \\
poá & po-á \xmark & po*á \cmark \\
impermeável & im*per*me-á*vel \xmark & im*per*me*á*vel \cmark \\
bioquímico & bi*o-quí*mi*co \xmark & bi*o*quí*mi*co \cmark \\
esôfago & e-sô*fa*go \xmark & e*sô*fa*go \cmark \\
gratuidade & gra*tu-i*da*de \xmark & gra*tu*i*da*de \cmark \\
piauiense & pi*au-i*en*se \xmark & pi*au-i*en*se \xmark \\
acuidade & a*cu-i*da*de \xmark & a*cu*i*da*de \cmark \\
destruidor & des*tru-i*dor \xmark & des*tru*i*dor \cmark \\
pentacampeão & pen*ta*cam*pe-ão \xmark & pen*ta*cam*pe*ão \cmark \\
prontuário & pron*tu-á*ri*o \xmark & pron*tu*á*ri*o \cmark \\
poliuretano & po*li-u*re*ta*no \xmark & po*li*u*re*ta*no \cmark \\
protozoário & pro*to*zo-á*ri*o \xmark & pro*to*zo*á*ri*o \cmark \\
reinvenção & re-in*ven*ção \xmark & re*in*ven*ção \cmark \\
afluência & a*flu-ên*ci*a \xmark & a*flu*ên*ci*a \cmark \\
fundiário & fun*di-á*ri*o \xmark & fun*di*á*ri*o \cmark \\
incendiário & in*cen*di-á*ri*o \xmark & in*cen*di*á*ri*o \cmark \\
itapuã & i*ta*pu-ã \xmark & i*ta*pu*ã \cmark \\
parcimônia & par*ci-mô*ni*a \xmark & par*ci*mô*ni*a \cmark \\
redemoinho & re*de*mo-i*nho \xmark & re*de*mo*i*nho \cmark \\

@@

inconsequência & in*con*se-quên*ci*a \xmark & in*con*se*quên*ci*a \cmark \\
pantaleão & pan*ta*le-ão \xmark & pan*ta*le*ão \cmark \\
poluidor & po*lu-i*dor \xmark & po*lu*i*dor \cmark \\
autodestruição & au*to*des*tru-i*ção \xmark & au*to*des*tru*i*ção \cmark \\
desunião & de*su*ni-ão \xmark & de*su*ni*ão \cmark \\
psicodélico & p.si*co*dé*li*co \xmark & psi*co*dé*li*co \cmark \\
saíra & sa-í*ra \xmark & sa*í*ra \cmark \\
subliminar & su.b-li*mi*nar \xmark & sub*li*mi*nar \cmark \\
ajuizado & a*ju-i*za*do \xmark & a*ju*i*za*do \cmark \\
antipoluição & an*ti*po*lu-i*ção \xmark & an*ti*po*lu*i*ção \cmark \\
gasômetro & ga-sô*me*tro \xmark & ga*sô*me*tro \cmark \\
hidroviário & hi*dro*vi-á*ri*o \xmark & hi*dro*vi*á*ri*o \cmark \\
miúdas & mi-ú*das \xmark & mi*ú*das \cmark \\
perequê & pe*re-quê \xmark & pe*re*quê \cmark \\
ciberespaço & ci*be.r-es*pa*ço \xmark & ci*be.r-es*pa*ço \xmark \\
condômino & con-dô*mi*no \xmark & con*dô*mi*no \cmark \\
jacuí & ja*cu-í \xmark & ja*cu*í \cmark \\
ministeriável & mi*nis*te*ri-á*vel \xmark & mi*nis*te*ri*á*vel \cmark \\
obituário & o*bi*tu-á*ri*o \xmark & o*bi*tu*á*ri*o \cmark \\
picuinha & pi*cu-i*nha \xmark & pi*cu-i*nha \xmark \\
psicodelismo & p.si*co*de*lis*mo \xmark & psi*co*de*lis*mo \cmark \\
suingue & su-in*gue \xmark & su-in*gue \xmark \\
apoteótico & a*po*te-ó*ti*co \xmark & a*po*te*ó*ti*co \cmark \\
caimento & ca-i*men*to \xmark & ca-i*men*to \xmark \\
cauim & cau-im \xmark & cau-im \xmark \\
estuário & es*tu-á*ri*o \xmark & es*tu*á*ri*o \cmark \\
flúor & flú-or \xmark & flú-or \xmark \\
incongruência & in*con*gru-ên*ci*a \xmark & in*con*gru*ên*ci*a \cmark \\
indissociável & in*dis*so*ci-á*vel \xmark & in*dis*so*ci*á*vel \cmark \\
mostruário & mos*tru-á*ri*o \xmark & mos*tru*á*ri*o \cmark \\
pneumologia & p.neu*mo*lo*gi*a \xmark & pneu*mo*lo*gi*a \cmark \\
proibitivo & pro-i*bi*ti*vo \xmark & pro*i*bi*ti*vo \cmark \\
reinterpretação & re-in*ter*pre*ta*ção \xmark & re*in*ter*pre*ta*ção \cmark \\
suinocultura & su-i*no*cul*tu*ra \xmark & su*i*no*cul*tu*ra \cmark \\
baiuca & bai-u*ca \xmark & bai-u*ca \xmark \\
conduíte & con*du-í*te \xmark & con*du*í*te \cmark \\
grandiloquência & gran*di*lo-quên*ci*a \xmark & gran*di*lo*quên*ci*a \cmark \\
impatriótico & im*pa*tri-ó*ti*co \xmark & im*pa*tri*ó*ti*co \cmark \\
megalômano & me*ga-lô*ma*no \xmark & me*ga*lô*ma*no \cmark \\
nipônico & ni-pô*ni*co \xmark & ni*pô*ni*co \cmark \\
pecuniário & pe*cu*ni-á*ri*o \xmark & pe*cu*ni*á*ri*o \cmark \\
psicopatologia & p.si*co*pa*to*lo*gi*a \xmark & psi*co*pa*to*lo*gi*a \cmark \\
reindexar & re-in*de*xar \xmark & re-in*de*xar \xmark \\
teleinformática & te*le-in*for*má*ti*ca \xmark & te*le*in*for*má*ti*ca \cmark \\
timbaúba & tim*ba-ú*ba \xmark & tim*ba*ú*ba \cmark \\
agônico & a-gô*ni*co \xmark & a*gô*ni*co \cmark \\
anômalo & a-nô*ma*lo \xmark & a*nô*ma*lo \cmark \\
auê & au-ê \xmark & au*ê \cmark \\
bestiário & bes*ti-á*ri*o \xmark & bes*ti*á*ri*o \cmark \\
copião & co*pi-ão \xmark & co*pi*ão \cmark \\
ensaística & en*sa-ís*ti*ca \xmark & en*sa*ís*ti*ca \cmark \\
fonoaudiólogo & fo*no*au*di-ó*lo*go \xmark & fo*no*au*di*ó*lo*go \cmark \\
imiscuir & i*mis*cu-ir \xmark & i*mis*cu-ir \xmark \\
jupiá & ju*pi-á \xmark & ju*pi*á \cmark \\
nagô & na-gô \xmark & na*gô \cmark \\
psicofarmacologia & p.si*co*far*ma*co*lo*gi*a \xmark & psi*co*far*ma*co*lo*gi*a \cmark \\
ruindade & ru-in*da*de \xmark & ru-in*da*de \xmark \\
sanduicheria & san*du-i*che*ri*a \xmark & san*du*i*che*ri*a \cmark \\
sociável & so*ci-á*vel \xmark & so*ci*á*vel \cmark \\
sublevação & su.b-le*va*ção \xmark & sub*le*va*ção \cmark \\
antiaéreo & an*ti*a-é*re*o \xmark & an*ti*a*é*re*o \cmark \\
atrabiliário & a*tra*bi*li-á*ri*o \xmark & a*tra*bi*li*á*ri*o \cmark \\
bôer & bô-er \xmark & bô-er \xmark \\
breviário & bre*vi-á*ri*o \xmark & bre*vi*á*ri*o \cmark \\
canônico & ca-nô*ni*co \xmark & ca*nô*ni*co \cmark \\
esfiha & es*fi-ha \xmark & es*fi-ha \xmark \\
influído & in*flu-í*do \xmark & in*flu-í*do \xmark \\
latifundiário & la*ti*fun*di-á*ri*o \xmark & la*ti*fun*di*á*ri*o \cmark \\
pajeú & pa*je-ú \xmark & pa*je*ú \cmark \\
psicopedagogia & p.si*co*pe*da*go*gi*a \xmark & psi*co*pe*da*go*gi*a \cmark \\
quinquênio & quin-quê*ni*o \xmark & quin*quê*ni*o \cmark \\
radiofrequência & ra*di*o*fre-quên*ci*a \xmark & ra*di*o*fre*quên*ci*a \cmark \\
tragicômico & tra*gi-cô*mi*co \xmark & tra*gi*cô*mi*co \cmark \\
vacuidade & va*cu-i*da*de \xmark & va*cu*i*da*de \cmark \\
autobiógrafo & au*to*bi-ó*gra*fo \xmark & au*to*bi*ó*gra*fo \cmark \\
beduíno & be*du-í*no \xmark & be*du*í*no \cmark \\
ergômetro & er-gô*me*tro \xmark & er*gô*me*tro \cmark \\
jataí & ja*ta-í \xmark & ja*ta*í \cmark \\
painho & pa-i*nho \xmark & pa*i*nho \cmark \\
pneumologista & p.neu*mo*lo*gis*ta \xmark & pneu*mo*lo*gis*ta \cmark \\
porciúncula & por*ci-ún*cu*la \xmark & por*ci*ún*cu*la \cmark \\
reutilizar & re-u*ti*li*zar \xmark & re-u*ti*li*zar \xmark \\
sainte & sa-in*te \xmark & sa-in*te \xmark \\
tsunami & t.su*na*mi \xmark & tsu*na*mi \cmark \\
zebuíno & ze*bu-í*no \xmark & ze*bu*í*no \cmark \\
aeroportuário & a*e*ro*por*tu-á*ri*o \xmark & a*e*ro*por*tu*á*ri*o \cmark \\
agroquímica & a*gro-quí*mi*ca \xmark & a*gro*quí*mi*ca \cmark \\
baraúna & ba*ra-ú*na \xmark & ba*ra*ú*na \cmark \\
catatônico & ca*ta-tô*ni*co \xmark & ca*ta*tô*ni*co \cmark \\
conteudista & con*te-u*dis*ta \xmark & con*te-u*dis*ta \xmark \\
continuísta & con*ti*nu-ís*ta \xmark & con*ti*nu*ís*ta \cmark \\
elegíaco & e*le*gí-a*co \xmark & e*le*gí*a*co \cmark \\
faraônico & fa*ra-ô*ni*co \xmark & fa*ra*ô*ni*co \cmark \\
hodômetro & ho-dô*me*tro \xmark & ho*dô*me*tro \cmark \\
ioiô & i.o-i.ô \xmark & i.o-i.ô \xmark \\
marruá & mar*ru-á \xmark & mar*ru*á \cmark \\
papaína & pa*pa-í*na \xmark & pa*pa*í*na \cmark \\
prostituído & pros*ti*tu-í*do \xmark & pros*ti*tu*í*do \cmark \\
reinquirir & re-in*qui*rir \xmark & re-in*qui*rir \xmark \\
reinterpretar & re-in*ter*pre*tar \xmark & re*in*ter*pre*tar \cmark \\
saião & sai-ão \xmark & sai*ão \cmark \\
samaúma & sa*ma-ú*ma \xmark & sa*ma*ú*ma \cmark \\
turboélice & tur*bo-é*li*ce \xmark & tur*bo*é*li*ce \cmark \\
ventoinha & ven*to-i*nha \xmark & ven*to*i*nha \cmark \\
alagoinha & a*la*go-i*nha \xmark & a*la*go*i*nha \cmark \\

@@

@@

@@

>>>>

aarônico & a*a-rô*ni*co \xmark & a*a*rô*ni*co \cmark \\
abadia & a*ba*di*a \cmark & a*ba*di-a \xmark \\
abdominoplastia & ab*do*mi*no*plas*ti*a \cmark & ab*do*mi*no*plas*ti-a \xmark \\
abecedário & a*be*ce*dá*ri.o \xmark & a*be*ce*dá*rio \cmark \\
abissínio & a*bis*sí*ni.o \xmark & a*bis*sí*nio \cmark \\
aboio & a*boi*o \cmark & a*boi-o \xmark \\
abrangência & a*bran*gên*ci.a \xmark & a*bran*gên*cia \cmark \\
abreugrafia & a*breu*gra*fi*a \cmark & a*breu*gra*fi-a \xmark \\
abrótea & a*bró*te.a \xmark & a*bró*tea \cmark \\
abstinência & abs*ti*nên*ci.a \xmark & abs*ti*nên*cia \cmark \\
abulia & a*bu*li*a \cmark & a*bu*li-a \xmark \\
abundância & a*bun*dân*ci*a \cmark & a*bun*dân*ci-a \xmark \\
acácia & a*cá*ci.a \xmark & a*cá*cia \cmark \\
academia & a*ca*de*mi*a \cmark & a*ca*de*mi-a \xmark \\
acatisia & a*ca*ti*si*a \cmark & a*ca*ti*si-a \xmark \\
acefalia & a*ce*fa*li*a \cmark & a*ce*fa*li-a \xmark \\
acéquia & a*cé*qui.a \xmark & a*cé*quia \cmark \\
acessório & a*ces*só*ri.o \xmark & a*ces*só*rio \cmark \\
acidemia & a*ci*de*mi*a \cmark & a*ci*de*mi-a \xmark \\
acônito & a-cô*ni*to \xmark & a*cô*ni*to \cmark \\
açoteia & a*ço*tei*a \cmark & a*ço*tei-a \xmark \\
acrobacia & a*cro*ba*ci*a \cmark & a*cro*ba*ci-a \xmark \\
acrofobia & a*cro*fo*bi*a \cmark & a*cro*fo*bi-a \xmark \\
acromegalia & a*cro*me*ga*li*a \cmark & a*cro*me*ga*li-a \xmark \\
actínio & ac*tí*ni.o \xmark & ac*tí*nio \cmark \\
acuidade & a*cu-i*da*de \xmark & a*cu-i*da*de \xmark \\
acurácia & a*cu*rá*ci.a \xmark & a*cu*rá*cia \cmark \\
adágio & a*dá*gi.o \xmark & a*dá*gio \cmark \\
adimplência & a*dim*plên*ci.a \xmark & a*dim*plên*cia \cmark \\
adjutório & ad*ju*tó*ri.o \xmark & ad*ju*tó*rio \cmark \\
adolescência & a*do*les*cên*ci.a \xmark & a*do*les*cên*cia \cmark \\
adultério & a*dul*té*ri.o \xmark & a*dul*té*rio \cmark \\
adventício & ad*ven*tí*ci.o \xmark & ad*ven*tí*cio \cmark \\
advérbio & ad*vér*bi.o \xmark & ad*vér*bio \cmark \\
adversário & ad*ver*sá*ri.o \xmark & ad*ver*sá*rio \cmark \\
advertência & ad*ver*tên*ci.a \xmark & ad*ver*tên*cia \cmark \\
advocacia & ad*vo*ca*ci*a \cmark & ad*vo*ca*ci-a \xmark \\
aéreo & a-é*re.o \xmark & a*é*reo \cmark \\
aeróbio & a*e*ró*bi.o \xmark & a*e*ró*bio \cmark \\
aerofobia & a*e*ro*fo*bi*a \cmark & a*e*ro*fo*bi-a \xmark \\
aerofotografia & a*e*ro*fo*to*gra*fi*a \cmark & a*e*ro*fo*to*gra*fi-a \xmark \\
aerografia & a*e*ro*gra*fi*a \cmark & a*e*ro*gra*fi-a \xmark \\
aeronomia & a*e*ro*no*mi*a \cmark & a*e*ro*no*mi-a \xmark \\
aeroportuário & a*e*ro*por*tu-á*ri.o \xmark & a*e*ro*por*tu*á*rio \cmark \\
aerovia & a*e*ro*vi*a \cmark & a*e*ro*vi-a \xmark \\
aeroviário & a*e*ro*vi-á*ri.o \xmark & a*e*ro*vi*á*rio \cmark \\
afasia & a*fa*si*a \cmark & a*fa*si-a \xmark \\
afélio & a*fé*li.o \xmark & a*fé*lio \cmark \\
afluência & a*flu-ên*ci.a \xmark & a*flu*ên*cia \cmark \\
aforia & a*fo*ri*a \cmark & a*fo*ri-a \xmark \\
agamia & a*ga*mi*a \cmark & a*ga*mi-a \xmark \\
agência & a*gên*ci.a \xmark & a*gên*cia \cmark \\
agenesia & a*ge*ne*si*a \cmark & a*ge*ne*si-a \xmark \\
aglossia & a*glos*si*a \cmark & a*glos*si-a \xmark \\
agnosia & ag*no*si*a \cmark & ag*no*si-a \xmark \\
agonia & a*go*ni*a \cmark & a*go*ni-a \xmark \\
agorafobia & a*go*ra*fo*bi*a \cmark & a*go*ra*fo*bi-a \xmark \\
agrário & a*grá*ri.o \xmark & a*grá*rio \cmark \\
agronomia & a*gro*no*mi*a \cmark & a*gro*no*mi-a \xmark \\
águia & á*gui.a \xmark & á*guia \cmark \\
aia & ai*a \cmark & ai-a \xmark \\

@@

aio & ai*o \cmark & ai-o \xmark \\
albergaria & al*ber*ga*ri*a \cmark & al*ber*ga*ri-a \xmark \\
albugínea & al*bu*gí*ne*a \cmark & al*bu*gí*ne-a \xmark \\
alcaidaria & al*cai*da*ri*a \cmark & al*cai*da*ri-a \xmark \\
alcaravia & al*ca*ra*vi*a \cmark & al*ca*ra*vi-a \xmark \\
alcaria & al*ca*ri*a \cmark & al*ca*ri-a \xmark \\
alcateia & al*ca*tei*a \cmark & al*ca*tei-a \xmark \\
alcoolemia & al*co*o*le*mi*a \cmark & al*co*o*le*mi-a \xmark \\
aldeia & al*dei*a \cmark & al*dei-a \xmark \\
aleatório & a*le*a*tó*ri.o \xmark & a*le*a*tó*rio \cmark \\
alegoria & a*le*go*ri*a \cmark & a*le*go*ri-a \xmark \\
alegria & a*le*gri*a \cmark & a*le*gri-a \xmark \\
aleia & a*lei*a \cmark & a*lei-a \xmark \\
aleivosia & a*lei*vo*si*a \cmark & a*lei*vo*si-a \xmark \\
alelopatia & a*le*lo*pa*ti*a \cmark & a*le*lo*pa*ti-a \xmark \\
aleluia & a*le*lui*a \cmark & a*le*lui-a \xmark \\
alergia & a*ler*gi*a \cmark & a*ler*gi-a \xmark \\
alergologia & a*ler*go*lo*gi*a \cmark & a*ler*go*lo*gi-a \xmark \\
aletria & a*le*tri*a \cmark & a*le*tri-a \xmark \\
alexia & a*le*xi*a \cmark & a*le*xi-a \xmark \\
alfaia & al*fai*a \cmark & al*fai-a \xmark \\
alfaiataria & al*fai*a*ta*ri*a \cmark & al*fai*a*ta*ri-a \xmark \\
alfarrábio & al*far*rá*bi.o \xmark & al*far*rá*bio \cmark \\
alforria & al*for*ri*a \cmark & al*for*ri-a \xmark \\
algaravia & al*ga*ra*vi*a \cmark & al*ga*ra*vi-a \xmark \\
algarvio & al*gar*vi*o \cmark & al*gar*vi-o \xmark \\
algofobia & al*go*fo*bi*a \cmark & al*go*fo*bi-a \xmark \\
alheio & a*lhei*o \cmark & a*lhei-o \xmark \\
aliáceo & a*li-á*ce.o \xmark & a*li*á*ceo \cmark \\

@@

alimária & a*li*má*ri.a \xmark & a*li*má*ria \cmark \\
alimentício & a*li*men*tí*ci.o \xmark & a*li*men*tí*cio \cmark \\
alínea & a*lí*ne.a \xmark & a*lí*nea \cmark \\
alívio & a*lí*vi.o \xmark & a*lí*vio \cmark \\

@@

alódio & a*ló*di.o \xmark & a*ló*dio \cmark \\
alometria & a*lo*me*tri*a \cmark & a*lo*me*tri-a \xmark \\
alopatia & a*lo*pa*ti*a \cmark & a*lo*pa*ti-a \xmark \\
alopecia & a*lo*pe*ci*a \cmark & a*lo*pe*ci-a \xmark \\
alquimia & al*qui*mi*a \cmark & al*qui*mi-a \xmark \\
alteia & al*tei*a \cmark & al*tei-a \xmark \\
alternância & al*ter*nân*ci.a \xmark & al*ter*nân*cia \cmark \\
altimetria & al*ti*me*tri*a \cmark & al*ti*me*tri-a \xmark \\
alucinatório & a*lu*ci*na*tó*ri.o \xmark & a*lu*ci*na*tó*rio \cmark \\
aluimento & a*lu-i*men*to \xmark & a*lu-i*men*to \xmark \\
aluir & a*lu-ir \xmark & a*lu*ir \cmark \\
alumínio & a*lu*mí*ni.o \xmark & a*lu*mí*nio \cmark \\
alvedrio & al*ve*dri*o \cmark & al*ve*dri-o \xmark \\
alvenaria & al*ve*na*ri*a \cmark & al*ve*na*ri-a \xmark \\
amásia & a*má*si.a \xmark & a*má*sia \cmark \\
amásio & a*má*si.o \xmark & a*má*sio \cmark \\

@@

ambidestria & am*bi*des*tri*a \cmark & am*bi*des*tri-a \xmark \\
ambrosia & am*bro*si*a \cmark & am*bro*si-a \xmark \\
ambulância & am*bu*lân*ci.a \xmark & am*bu*lân*cia \cmark \\
ambulatório & am*bu*la*tó*ri.o \xmark & am*bu*la*tó*rio \cmark \\
ameia & a*mei*a \cmark & a*mei-a \xmark \\
amélia & a*mé*li.a \xmark & a*mé*lia \cmark \\
amêndoa & a*mên*do.a \xmark & a*mên*doa \cmark \\
amendoim & a*men*do-im \xmark & a*men*do*im \cmark \\
amenorreia & a*me*nor*rei*a \cmark & a*me*nor*rei-a \xmark \\
amerício & a*me*rí*ci.o \xmark & a*me*rí*cio \cmark \\
ameríndio & a*me*rín*di.o \xmark & a*me*rín*dio \cmark \\

@@

@@

amontoa & a*mon*to*a \cmark & a*mon*to-a \xmark \\
ampelografia & am*pe*lo*gra*fi*a \cmark & am*pe*lo*gra*fi-a \xmark \\
anaeróbio & a*na*e*ró*bi.o \xmark & a*na*e*ró*bio \cmark \\
anafilaxia & a*na*fi*la*xi*a \cmark & a*na*fi*la*xi-a \xmark \\
analgesia & a*nal*ge*si*a \cmark & a*nal*ge*si-a \xmark \\
analogia & a*na*lo*gi*a \cmark & a*na*lo*gi-a \xmark \\
anarquia & a*nar*qui*a \cmark & a*nar*qui-a \xmark \\
anatomia & a*na*to*mi*a \cmark & a*na*to*mi-a \xmark \\
androfobia & an*dro*fo*bi*a \cmark & an*dro*fo*bi-a \xmark \\
androginia & an*dro*gi*ni*a \cmark & an*dro*gi*ni-a \xmark \\
andrologia & an*dro*lo*gi*a \cmark & an*dro*lo*gi-a \xmark \\
anedonia & a*ne*do*ni*a \cmark & a*ne*do*ni-a \xmark \\
anelídeo & a*ne*lí*de.o \xmark & a*ne*lí*deo \cmark \\
anemia & a*ne*mi*a \cmark & a*ne*mi-a \xmark \\
anemofilia & a*ne*mo*fi*li*a \cmark & a*ne*mo*fi*li-a \xmark \\
anestesia & a*nes*te*si*a \cmark & a*nes*te*si-a \xmark \\
anestesiologia & a*nes*te*si*o*lo*gi*a \cmark & a*nes*te*si*o*lo*gi-a \xmark \\
aneuploidia & a*neu*ploi*di*a \cmark & a*neu*ploi*di-a \xmark \\
anfíbio & an*fí*bi.o \xmark & an*fí*bio \cmark \\
anfibologia & an*fi*bo*lo*gi*a \cmark & an*fi*bo*lo*gi-a \xmark \\
angiologia & an*gi*o*lo*gi*a \cmark & an*gi*o*lo*gi-a \xmark \\
angioplastia & an*gi*o*plas*ti*a \cmark & an*gi*o*plas*ti-a \xmark \\
angústia & an*gús*ti.a \xmark & an*gús*tia \cmark \\
anisogamia & a*ni*so*ga*mi*a \cmark & a*ni*so*ga*mi-a \xmark \\
anisotropia & a*ni*so*tro*pi*a \cmark & a*ni*so*tro*pi-a \xmark \\
anistia & a*nis*ti*a \cmark & a*nis*ti-a \xmark \\
aniversário & a*ni*ver*sá*ri.o \xmark & a*ni*ver*sá*rio \cmark \\
anodinia & a*no*di*ni*a \cmark & a*no*di*ni-a \xmark \\
anomalia & a*no*ma*li*a \cmark & a*no*ma*li-a \xmark \\
anomia & a*no*mi*a \cmark & a*no*mi-a \xmark \\
anorexia & a*no*re*xi*a \cmark & a*no*re*xi-a \xmark \\
anosmia & a*nos*mi*a \cmark & a*nos*mi-a \xmark \\
anoxia & a*no*xi*a \cmark & a*no*xi-a \xmark \\
anseio & an*sei*o \cmark & an*sei-o \xmark \\

@@

antecedência & an*te*ce*dên*ci.a \xmark & an*te*ce*dên*cia \cmark \\
antinomia & an*ti*no*mi*a \cmark & an*ti*no*mi-a \xmark \\
antipatia & an*ti*pa*ti*a \cmark & an*ti*pa*ti-a \xmark \\
antiquário & an*ti-quá*ri.o \xmark & an*ti*quá*rio \cmark \\

@@

antissepsia & an*tis*sep*si*a \cmark & an*tis*sep*si-a \xmark \\
antologia & an*to*lo*gi*a \cmark & an*to*lo*gi-a \xmark \\
antonomásia & an*to*no*má*si.a \xmark & an*to*no*má*sia \cmark \\
antropofagia & an*tro*po*fa*gi*a \cmark & an*tro*po*fa*gi-a \xmark \\
antropologia & an*tro*po*lo*gi*a \cmark & an*tro*po*lo*gi-a \xmark \\
antropometria & an*tro*po*me*tri*a \cmark & an*tro*po*me*tri-a \xmark \\
antroponímia & an*tro*po*ní*mi.a \xmark & an*tro*po*ní*mia \cmark \\
antroposofia & an*tro*po*so*fi*a \cmark & an*tro*po*so*fi-a \xmark \\
anuário & a*nu-á*ri.o \xmark & a*nu*á*rio \cmark \\
anuência & a*nu-ên*ci.a \xmark & a*nu*ên*cia \cmark \\
anúncio & a*nún*ci.o \xmark & a*nún*cio \cmark \\
apanágio & a*pa*ná*gi.o \xmark & a*pa*ná*gio \cmark \\
aparência & a*pa*rên*ci.a \xmark & a*pa*rên*cia \cmark \\
apatia & a*pa*ti*a \cmark & a*pa*ti-a \xmark \\
apendicectomia & a*pen*di*cec*to*mi*a \cmark & a*pen*di*cec*to*mi-a \xmark \\
apetência & a*pe*tên*ci.a \xmark & a*pe*tên*cia \cmark \\
aplasia & a*pla*si*a \cmark & a*pla*si-a \xmark \\
apneia & ap*nei*a \cmark & ap*nei-a \xmark \\
apofonia & a*po*fo*ni*a \cmark & a*po*fo*ni-a \xmark \\
apoio & a*poi*o \cmark & a*poi-o \xmark \\
apologia & a*po*lo*gi*a \cmark & a*po*lo*gi-a \xmark \\
apoplexia & a*po*ple*xi*a \cmark & a*po*ple*xi-a \xmark \\
aporia & a*po*ri*a \cmark & a*po*ri-a \xmark \\
aposentadoria & a*po*sen*ta*do*ri*a \cmark & a*po*sen*ta*do*ri-a \xmark \\
apostasia & a*pos*ta*si*a \cmark & a*pos*ta*si-a \xmark \\
apraxia & a*pra*xi*a \cmark & a*pra*xi-a \xmark \\
aquário & a-quá*ri.o \xmark & a*quá*rio \cmark \\
aquícola & a-quí*co*la \xmark & a*quí*co*la \cmark \\
aquiescência & a*qui*es*cên*ci.a \xmark & a*qui*es*cên*cia \cmark \\
aquileia & a*qui*lei*a \cmark & a*qui*lei-a \xmark \\
arábias & a*rá*bi.as \xmark & a*rá*bi.as \xmark \\
